%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Lachaise Assignment
% LaTeX Template
% Version 1.0 (26/6/2018)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Marion Lachaise & Fran\UTF{00C3}§ois F\UTF{00C3}\UTF{00A9}votte
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{article}
%German language
\usepackage[ngerman]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc} 
\usepackage{cancel}
\usepackage{xifthen}
\usepackage{venndiagram}
\usepackage{pgfplots}
\usepackage{wrapfig}
\usepackage{comment}
\usepackage{amsmath}
\usepackage[nolist]{acronym}
\usepackage{xcolor}
\usepackage{algorithmic}
\usepackage{multicol}
\usepackage{csquotes}
\usepackage{tikz}
\usepackage{hyperref}
\usetikzlibrary{calc,shapes.multipart,chains,arrows}
\usepackage{titlesec}


\usepackage{listings}
\usepackage{xcolor}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
	backgroundcolor=\color{backcolour},   
	commentstyle=\color{codegreen},
	keywordstyle=\color{magenta},
	numberstyle=\tiny\color{codegray},
	stringstyle=\color{codepurple},
	basicstyle=\ttfamily\footnotesize,
	breakatwhitespace=false,         
	breaklines=true,                 
	captionpos=b,                    
	keepspaces=true,                 
	numbers=left,                    
	numbersep=5pt,                  
	showspaces=false,                
	showstringspaces=false,
	showtabs=false,                  
	tabsize=2
}

\lstset{style=mystyle}


\input{structure.tex} % Include the file specifying the document structure and custom commands
%----------------------------------------------------------------------------------------
%	ASSIGNMENT INFORMATION
%----------------------------------------------------------------------------------------

\title{GDPR Compliant Cloud Data Storage and Processing Engine as a Service\\[0.4em]\smaller{}\smaller{}Cryptographic Protocols} 
\author{
	Mats Kockmeyer\\ \texttt{Mats.Kockmeyer2@stud.hs-flensburg.de}\\\\
	Felix Janke\\ \texttt{Felix.Janke2@stud.hs-flensburg.de}
} 

\date{Hochschule Flensburg --- \today} % University, school and/or department name(s) and a date

%----------------------------------------------------------------------------------------
\allowdisplaybreaks
\definecolor{light}{RGB}{138, 216, 203}
\begin{document}
\begin{acronym}
\acro{CSP}{Cloud Service Provider}
\acro{DRAM}{Dynamic Random Access Memory}
\acro{PRM}{Processor Reserved Memory}
\acro{EPC}{Enclave Page Cache}
\acro{SQL}{Structured Query Language}
\end{acronym}

\maketitle % Print the title

\newcommand{\acr}[1]{\acs{#1} (\aclu{#1})}

 \newcommand{\wip}[1]{
  \ifthenelse{\isempty{#1}}%
    {\colorbox{yellow!50}{$\boxast $}}% if #1 is empty
    {\colorbox{yellow!50}{$\boxast $}\textit{\smaller{} #1} }% if #1 is not empty
   }


%Input sections
\input{sections/project}
\input{sections/company}
\input{sections/requirements}
\input{sections/architecture}
%------------------------------------------------
\begin{thebibliography}{9}
%\bibitem{blsPaper}
%Boneh, D., Drijvers, M., \& Neven, G. BLS Multi-Signatures With Public-Key Aggregation.	
\bibitem{sgx-bibel}
Costan, Victor, and Srinivas Devadas. 2016. Intel SGX Explained. http://eprint.iacr.org/2016/086 (November 8, 2019).

\bibitem{sgx-performance}
Weichbrodt, Nico, Pierre-Louis Aublin, and Rüdiger Kapitza. 2018. “Sgx-Perf: A Performance Analysis Tool for Intel SGX Enclaves.” In Proceedings of the 19th International Middleware Conference on - Middleware ’18, Rennes, France: ACM Press, 201–13. http://dl.acm.org/citation.cfm?doid=3274808.3274824 (January 21, 2020).


\end{thebibliography}
\end{document}
